##### Rick Jones feature

If you specify a column in a data frame by:  
```{r}
    df["column.name"]
```  
it *preserves* the original data structure.  
But if you specify a column by:
```{r}
    df[ , "column.name"] 
```  
it *simplifies* the data structure to the simplest possible data structure that can answer the question.


##### Patrick Kilduff wuz here

Applying *apply* in a way that might frustrate Rick

```{r}
   cat(sapply(letters , function(a) sapply(letters , 
    function(b) sapply(letters , 
    function(c) sapply(letters , 
    function(d) paste(a, b, c, d, letters, "\n", sep=""))))))
```

##### Steve Mortimer

The assignment operator can actually work in either direction. Weird.

```{r weird_assignment_direction}
	x <- 6 -> y
```

#### from Vicki Garcia

I use this a lot to exclude missing values, which messes up some analyses

```{r}
df2=df1[complete.cases(df1[,"column.name"]),]
```

### from Tim Dunbar
```{r}
my favorite is the splom command in the lattice library, it's a really good way to see which corellations exist
```

### Keith Brown has returned from the dead
'''{r}
The R package "party" should play an important role in out project: The core of the package is ctree(), an implementation of conditional inference trees which embed tree-structured regression models into a well defined theory of conditional inference procedures. This non-parametric class of regression trees is applicable to all kinds of regression problems, including nominal, ordinal, numeric, censored as well as multivariate response variables and arbitrary measurement scales of the covariates. Based on conditional inference trees, cforest() provides an implementation of Breiman's random forests. The function mob() implements an algorithm for recursive partitioning based on parametric models (e.g. linear models, GLMs or survival regression) employing parameter instability tests for split selection. Extensible functionality for visualizing tree-structured regression models is available.